A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 0_main.tex
caption and some random changes. - Jun

\begin{document}
\baselineskip11pt % SPM template

\begin{frontmatter} % SPM template

@@

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu{\corref{cor1}}^*}
\ead{j.wu-1@tudelft.nl}
\author[cuhk]{Charlie Wang}
% \ead{cwang@mae.cuhk.edu.hk}
\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
%Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which avoids extreme bead width deviation from the nozzle size, and limits the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 slices.
%This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

>>>>

\begin{document}
\baselineskip11pt

\begin{frontmatter}

@@

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu\corref{cor1}}
\ead{j.wu-1@tudelft.nl}
\cortext[cor1]{Corresponding author}
\author[cuhk]{Charlie Wang}
% \ead{cwang@mae.cuhk.edu.hk}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities 
%Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
%Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which avoids extreme bead width deviation from the nozzle size, and limits the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 slices.
%This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

### 2019-08-30 10_applications.tex
caption and some random changes. - Jun

For architectural models and casings, the prevention of over- and underfill is expected to make them stronger. 
For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
Gears and similar mechanical parts could benefit from the prevention of under- and overfill regions and the distributed bead widths because the more homogeneous extrusion widths cause the part to more closely 
conform to the presumed homogenized material properties of FDM products.

Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties closer to expectation.
For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}), which are accurately densely filled using our framework.

Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

>>>>

For architectural models and casings, the prevention of over- and underfill is expected to make them stronger. 
For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
For gears and similar mechanical parts that are designed with finite element analysis, the less variation in extrusion widths is closer to the assumptions under fast analysis (e.g. using homogenization~\cite{Liu2016CAD}).

Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}). 
These structures are accurately densely filled using our framework.
Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
\jun{is it easy to embed the color lengend here so readers don't have to flip}
}
\label{applications_overview}
\end{figure*}

### 2019-08-30 4_method.tex
caption and some random changes. - Jun

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--bead-count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transitions-applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-transitioning-filtering--result-uoc.pdf}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, central edges marked in blue, other edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) where the bead count transitions.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning.png}
\caption{Without transitioning}
\end{subfigure}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning.png}
\caption{Transitioning}
\end{subfigure}
\caption{
Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
}
\label{transitions}
\end{figure}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--bead-count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transitions-applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-transitioning-filtering--result-uoc.pdf}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, central edges marked in blue, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked edges (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) where the bead count transitions.
\subref{beading_transitioning_filtering__filtered} We then filter out regions which exhibit frequent transition.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning.png}
\caption{Without transitioning}
\end{subfigure}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning.png}
\caption{Transitioning}
\end{subfigure}
\caption{
Sharp turns around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
}
\label{transitions}
\end{figure}

### 2019-08-30 5_generalization.tex
caption and some random changes. - Jun

\subsection{Beading schemes}
We introduce several beading schemes which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
We also introduce new beading schemes which produce toolpaths with less extremal widths compared to techniques from existing literature.

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
See \cref{formula_centered}.

>>>>

% \subsection{Beading schemes}
We introduce several beading schemes which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
We also introduce new beading schemes which produce toolpaths with less extremal widths compared to techniques from existing literature.

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}.
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
See \cref{formula_centered}.

### 2019-08-30 6_validation.tex
caption and some random changes. - Jun

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

@@

\caption{
Results of computational analysis of the results from applying the uniform width technique and various beading schemes using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
\end{subfigure}
\caption{
Visualization of the overfills and underfills (top) and the widths (bottom) for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

@@

\caption{
Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}
